---
title: "Stats By Jaiden"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    highlight: kate
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(gt)
library(readxl)
library(ggrepel)

supercoach_scoring_system <- read_excel("~/supercoach scoring system.xlsx")
```

```{r, echo=FALSE}
url_logo <- "https://raw.githubusercontent.com/jaidenpopowski/logos/main/Competitions/SuperCoachBBL.png"
```
# SuperCoach AFL: Deriving the complex scoring system
<center><img src="`r url_logo`"></center>

I've always been intrigued by the AFL SuperCoach game. Players' scores are determined by a variety of playing statistics for each game. These include disposals and respective efficiency, contested and uncontested marks, goals, hitouts to advantage, and many more. This scoring is said to reflect the real game of AFL, where acts that help win the game rewarded. Another step is that each game is scaled to 3300 points per game. Perhaps the most complicated part is the time aspect, where players can earn big points by helping their team to a close win late in the game.

Unlocking the secrets behind how SuperCoach AFL is scored will give better insights to the community and help with player selection. How do certain players achieve such high averages? And what causes big differences between SuperCoach scores and the more simple system of AFL Fantasy?


## What we know about scoring
From the SuperCoach T&C's from 2022, we have the following scoring breakdown:
```{r,echo=F}
supercoach_scoring_system %>% 
  select(1,2) %>% 
  gt()
```
What do these even mean?
&nbsp;
<hr />
<p style="text-align: center;">Written by <a href="https://twitter.com/jaiden_popowski">Jaiden Popowski</a></p>
<p style="text-align: center;"><span style="color: #808080;"><em>jaidenstats@gmail.com</em></span></p>

<!-- Add icon library -->
<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/4.7.0/css/font-awesome.min.css">

<!-- Add font awesome icons -->
<p style="text-align: center;">
    <a href="https://twitter.com/jaiden_popowski">Twitter</a>
    <a>   |   </a>
    <a href="https://github.com/jaidenpopowski">GitHub</a>
</p>

&nbsp;